---
title: "Alcohol vs Seat choice"
author: "Damian Earp"
date: "Summer 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  judging by the graph shown above, it appears that of the three places people chose to sit, the back seat has the most alcohol consumed compared to the frond and middle seats. probably to not get caught.
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The second graph seems to have the box go inwards until it reaches the median of the back, front, and middle seats. The back having a median of about 4, the front on the 0, and middle about 1 maybe 2.

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=davisdata)
```
This numerical summary shows that the back row have 32 people and the front row has 33, while the Middle row had more then double! The back row's First quarter (Q1) being just under 1 at .75. As we look at the mean, we can see that comparing the Middle row with the back, the back row has roughly triple the consumption compared to the middle row.
## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

As seen in the Inferential test, the probability is 0.000116, which is extremely low, so we reject the null hypnosis! 


## Conclusions


